---
title: "Ontario_preamble"
author: "achubaty"
date: "30 October 2020"
output: pdf_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see https://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path("/home/achubaty/Documents/GitHub/FOR-CAST/Ontario_AOU/modules"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 10)

parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("Ontario_preamble")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE}
df_params <- moduleParams("Ontario_preamble", "/home/achubaty/Documents/GitHub/FOR-CAST/Ontario_AOU/modules")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("Ontario_preamble", "/home/achubaty/Documents/GitHub/FOR-CAST/Ontario_AOU/modules")` may be sufficient.

```{r moduleInputs, echo = FALSE}
df_inputs <- moduleInputs("Ontario_preamble", "/home/achubaty/Documents/GitHub/FOR-CAST/Ontario_AOU/modules")
knitr::kable(df_inputs)
```

### Historic and projected climate data

`ClimateNA` was used to get monthly historic and projected climate variables for Ontario.

1. DEM from GEOTOPO15 product
2. Climate data using ClimateNA with projected CCSM4 RCP 4.5 and 8.5
3. Assemble MDC raster stacks using:

```{r makeMDC, echo = TRUE, eval=FALSE}
#install_github('PredictiveEcology/climateData@development')

library(raster)
library(climateData)

mdc_historic <- makeMDC("~/data/climate/ClimateNA_data/historic_1991-2019/Ontario", 1991:2019)
writeRaster(mdc_historic, "~/GitHub/FOR-CAST/Ontario_AOU/inputs/mdc_historic_1991-2019.grd")

mdc_future45 <- makeMDC("~/data/climate/ClimateNA_data/future_2011-2100/CCSM4_RCP45/Ontario", 2011:2100)
writeRaster(mdc_future45, "~/GitHub/FOR-CAST/Ontario_AOU/inputs/mdc_future_CCSM4_RCP45_2011-2100.grd")

mdc_future85 <- makeMDC("~/data/climate/ClimateNA_data/future_2011-2100/CCSM4_RCP85/Ontario", 2011:2100)
writeRaster(mdc_future85, "~/GitHub/FOR-CAST/Ontario_AOU/inputs/mdc_future_CCSM4_RCP85_2011-2100.grd")
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- moduleOutputs("Ontario_preamble", "/home/achubaty/Documents/GitHub/FOR-CAST/Ontario_AOU/modules")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
