---
title: "Ontario_preamble"
author: "Alex Chubaty"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, results = "hold")
```

# Overview

Define the AOU and ROF study areas, subsetting ROF by ecozone, and prepare species equivalency table for running LandR-fireSense simulations.

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, eval = TRUE, echo = FALSE, message=FALSE, warning=FALSE}
df_params <- SpaDES.core::moduleParams("Ontario_preamble", "..")
knitr::kable(df_params)
```

# Events

This module consists of a single `init` event that performs all the data preparation.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData(...)` may be sufficient.

```{r moduleInputs, eval = TRUE, echo = FALSE, message=FALSE, warning=FALSE}
df_inputs <- SpaDES.core::moduleInputs("Ontario_preamble", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE}
df_outputs <- SpaDES.core::moduleOutputs("Ontario_preamble", "..")
knitr::kable(df_outputs)
```

# Links to other modules

LandR Biomass suite of modules and the fireSense suite of modules.
